### 2015-04-20 rapport/formalism.tex
rapport_200415

Figure~\ref{} gives an example of a stencil computation $s(R,w,D,\text{exp},\mathcal{N})$, where $\mathcal{M}(V,E)$ is a two dimensional Cartesian mesh. A single domain $D$ is defined in this example and is composed of cells formed by a cycle of four vertices $v \in V$ and four edges $e \in E$. Furthermore, in this example $R=\{A\}$, $w=B$, and for $(x,y) \in D$ the neighborhood function is 
\begin{equation*}
\mathcal{N} : (x,y) \rightarrow \{(x,y+1),(x,y-1),(x+1,y),(x-1,y)\}.
\end{equation*}
Finally, the numerical expression of this example is 
\begin{equation*}
\text{exp}(A(x,y),A(\mathcal{N}(x,y)) = B(x,y) = A(x,y)+(A(x,y+1)+A(x,y-1)+A(x+1,y)+A(x-1,y))/4.
\end{equation*}

>>>>

Figure~\ref{fig:ex} gives an example of a stencil computation $s(R,w,D,\text{exp},\mathcal{N})$, where $\mathcal{M}(V,E)$ is a two dimensional Cartesian mesh. A single domain $D$ is defined in this example and is composed of cells formed by a cycle of four vertices $v \in V$ and four edges $e \in E$. Furthermore, in this example $R=\{A\}$, $w=B$, and for $(x,y) \in D$ the neighborhood function is 
\begin{equation*}
\mathcal{N} : (x,y) \rightarrow \{(x,y+1),(x,y-1),(x+1,y),(x-1,y)\}.
\end{equation*}
Finally, the numerical expression of this example is 
\begin{equation*}
\text{exp}(A(x,y),A(\mathcal{N}(x,y)) = B(x,y) = A(x,y)+(A(x,y+1)+A(x,y-1)+A(x+1,y)+A(x-1,y))/4.
\end{equation*}

\begin{figure}[!h]\begin{center}
  \resizebox{8cm}{!}{\includegraphics{./images/example.pdf}}
  \caption{Example of a stencil computation.}
  \label{fig:ex}
\end{center}\end{figure}
